---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tcgaViz

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/tcgaViz)](https://CRAN.R-project.org/package=tcgaViz)
[![R build status](https://github.com/ecamenen/tcgaViz/workflows/R-CMD-check/badge.svg)](https://github.com/ecamenen/tcgaViz/actions)
[![Codecov test coverage](https://codecov.io/gh/ecamenen/tcgaViz/branch/develop/graph/badge.svg)](https://codecov.io/gh/ecamenen/tcgaViz?branch=master)
<!-- badges: end -->

A visualization tool to depict proportions of immune cells in any tumor relative to the average expression of any gene (or signature).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ecamenen/tcgaViz")
```

## Docker

###### Pull
```
docker pull eucee/tcga-viz
```

###### (Local installation)
```
docker build -t tcga-viz .
```

###### Run in command-line
```
docker run --rm \
  -p 127.0.0.1:8787:8787 \
  -v $(pwd):/home/rstudio \
  -e ROOT=TRUE \
  -e DISABLE_AUTH=true \
  tcga-viz
```

## Example

###### Load two data sets
(with the same cancer type and TCGA sample identifiers)
```{r setup}
library(tcgaViz)
library(ggpubr, quietly = TRUE)
data(tcga)
head(tcga$genes)
head(tcga$cells$Cibersort_ABS)
```

###### Violin plot of cell subtypes
(and significance of a Wilcoxon adjusted test according to the expression
 level [high or low] of a selected gene)
```{r plot}
df <- (convert2biodata(
  algorithm = "Cibersort_ABS",
  disease = "breast invasive carcinoma",
  tissue = "Primary Tumor",
  gene_x = "A"
))
stats <- calculate_pvalue(df)
plot_violin(df, stats = stats)
```
